Bayesian Rate Estimation

### 2012-08-13 many.tex
Comment on normalization.

We can marginalize the posterior over the flags, $f_i$, obtaining
\begin{equation}
  \label{eq:rate-shape-posterior}
  p\left( R_f, R_b, \theta | d \right) = \sum_{\mathset{f_i} \in
    \mathset{0,1}^N} p\left( \mathset{f_i}, R_f, R_b, \theta | d \right)
  \propto \prod_{i} \left[ R_f \hat{f}\left(x_i, \theta\right) + R_b
    \hat{b}\left( x_i, \theta\right) \right] \exp\left[-\left( R_f +
      R_b \right) \right] \frac{p(\theta)}{\sqrt{R_f R_b}}.
\end{equation}
This expression is useful if we are only interested in rates and not
the probability that any particular event is foreground or background.
Unlike the full posterior (Eq.~\eqref{eq:posterior}),
Eq.~\eqref{eq:rate-shape-posterior} contains only continuous
parameters.

>>>>

We can marginalize the posterior over the flags, $f_i$, obtaining
\begin{equation}
  \label{eq:rate-shape-posterior}
  p\left( R_f, R_b, \theta | d \right) = \sum_{\mathset{f_i} \in
    \mathset{0,1}^N} p\left( \mathset{f_i}, R_f, R_b, \theta | d \right)
  \propto \prod_{i} \left[ R_f \hat{f}\left(x_i, \theta\right) + R_b
    \hat{b}\left( x_i, \theta\right) \right] \exp\left[-\left( R_f +
      R_b \right) \right] \frac{p(\theta)}{\sqrt{R_f R_b}}.
\end{equation}
\ilya{[Note: some of the expressions here aren't really properly normalized -- should check carefully which ones are, and replace $=$ by $\propto$ for the others.]}
This expression is useful if we are only interested in rates and not
the probability that any particular event is foreground or background.
Unlike the full posterior (Eq.~\eqref{eq:posterior}),
Eq.~\eqref{eq:rate-shape-posterior} contains only continuous
parameters.
